### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@5fff1ce67f2c5c2c640f8d6823454793f1667aba 🚀
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@cb9c3acc708fb9039a60bd90e98617b795b3246c 🚀

wherein \(\text{tp}\) is the number of interactions predicted as
positive, \(\text{tn}\) is the number of non-interactions predicted as
negative, \(\text{fp}\) is the number of non-interactions predicted as
positive, and \(\text{fn}\) is the number of interactions predicted as
negative. Almost all measures based on the confusion matrix express
rates of error or success as proportions, and therefore the values of
these components matter in a \emph{relative} way.

@@

In this section, we will change the values of \(b\) abd \(s\) for a
given value of \(\rho\), and see how the values of common performance
measures for binary classification are affected.

>>>>

wherein \(\text{tp}\) is the number of interactions predicted as
positive, \(\text{tn}\) is the number of non-interactions predicted as
negative, \(\text{fp}\) is the number of non-interactions predicted as
positive, and \(\text{fn}\) is the number of interactions predicted as
negative. Almost all measures based on the confusion matrix express
rates of error or success as proportions, and therefore the values of
these components matter in a \emph{relative} way. At a coarse scale, a
classifier is \emph{accurate} when the trace of the matrix divided by
the sum of the matrix is close to 1, with other measures focusing on
different ways in which the classifer is wrong.

@@

In this section, we will change the values of \(b\) abd \(s\) for a
given value of \(\rho\), and see how the values of common performance
measures for binary classification are affected. Specifically, we will
focus on four quantities: the accuracy
(\((\text{tp}+\text{tn})/(\text{tp}+\text{tn}+\text{fp}+\text{fn})\)),
the \emph{balanced} accuracy
(\(\text{tp}/(2(\text{tp}+\text{fn}))+\text{tn}/(2(\text{tn}+\text{fp}))\)),
Youden's J
(\(\text{tp}/(\text{tp}+\text{fn})+\text{tn}/(\text{tn}+\text{fp})-1\)),
and the \(F_1\) score (\(2\text{tp}/(2\text{tp}+\text{fp}+\text{fn})\)).
